BarnebyLives':' an R package to create herbarium specimen labels and digital data sheets

### 2023-11-20 manuscript/manuscript_APPS.rmd
addressing epithets

# how many of my genera were outdated?
genus_incongruence <- data_p %>% 
  sf::st_drop_geometry() %>% 
  filter(POW_Genus != 'NOT FOUND') %>% 
  filter(POW_Genus != Genus)  %>% 
  select(Collection_number, Full_name, Genus, POW_Genus)

# the mismatch between POW genus and not
genus_mismatch <- data_p %>% 
  sf::st_drop_geometry() %>% 
  filter(POW_Genus != 'NOT FOUND') %>% 
  filter(POW_Genus != Genus) %>% 
  select(Collection_number, Full_name, Genus, POW_Genus) %>% 
  mutate(Situation = 
    case_when(
      Genus %in% c('Pleuraphis', 'Glandularia') ~ 'Preferred', # check Pleuraphis, i am confused on this still....
      Genus %in% c('Oenothera', 'Cryptantha', 'Ivesia', 'Lotus', 'Polygala', 'Minuartia',
                    'Pseudostellaria', 'Achnatherum', 'Scirpus', 'Peritoma', 'Arenaria', 
                    'Spartina', 'Polygonum', 'Atriplex', 'Cymopterus', 'Trisetum', 'Bahia', 
                   'Oryzopsis', 'Potentilla', 'Pascopyrum'
                    ) ~ 'Outdated',
      Genus %in% c('Vaccinium', 'Eleocharis') ~ 'Internal_Error',
      .default = 'Typo'
    ),
    Situation = if_else(Full_name == 'Oenothera caespitosa Nutt.', 'Internal_Error', Situation))

@@

epithet_diff <- data_p %>% 
  sf::st_drop_geometry() %>% 
  filter(Epithet != POW_Epithet, !Full_name %in% unique(genus_mismatch$Full_name )) %>% 
  select(Collection_number, Full_name, Epithet, POW_Epithet)

@@

... XX were preferred by author.

the number of misspelled binomials were XX (% percent).

@@

>>>>

# the mismatch between POW genus and not
genus_mismatch <- data_p %>% 
  sf::st_drop_geometry() %>% 
  filter(POW_Genus != 'NOT FOUND') %>% 
  filter(POW_Genus != Genus) %>% 
  select(Collection_number, Full_name, Genus, POW_Genus) %>% 
  mutate(Situation = 
    case_when(
      Genus %in% c('Glandularia', 'Oenothera', 'Chamerion') ~ 'Preferred',
      # check Pleuraphis, i am confused on this still....
      Genus %in% c('Cryptantha', 'Ivesia', 'Lotus', 'Polygala', 'Minuartia', 'Pleuraphis',
                    'Pseudostellaria', 'Achnatherum', 'Scirpus', 'Peritoma', 'Arenaria', 
                    'Spartina', 'Polygonum', 'Atriplex', 'Cymopterus', 'Trisetum', 'Bahia', 
                   'Oryzopsis', 'Potentilla', 'Pascopyrum'
                    ) ~ 'Outdated',
      Genus %in% c('Vaccinium', 'Eleocharis') ~ 'Internal_Error',
      .default = 'Typo'
    ),
    Situation = if_else(Full_name == 'Oenothera caespitosa Nutt.', 'Internal_Error', Situation))

@@

epithet_diff <- data_p %>% 
  sf::st_drop_geometry() %>% 
  filter(Epithet != POW_Epithet, !Full_name %in% 
           unique(c( genera_mispelled$Full_name,  genus_mismatch$Full_name))) %>% 
  select(Collection_number, Full_name, Epithet, POW_Genus, POW_Epithet, POW_Infraspecies) %>% 
  distinct(Full_name, .keep_all = T) %>%  # do we record repeat collections ?
  mutate(Situation = 
           case_when(
             Collection_number %in% c('1217') ~ 'Spelling',
             Collection_number %in% c('1588', '2445', '2777', '1337', '2412', '2748', 
                                      '2652', '2805', '2194', '2040', '2039', '2403', '2328') ~ 'Outdated',
             Collection_number %in% c('2326', '2038') ~ 'Internal_Error' ,
             Collection_number %in% c('2110') ~ 'Preferred'

           )
  )

srm(Family_in, Family_out)
```

@@

BL was able to identify 41 misspellings ...
BL made `r nrow(family_incongruence)` suggestions on naming, 
where an incorrect family was entered, and `r sum(genus_mismatch$Situation=='Outdated', na.rm = T)` instance of an outdated circumscription applied. BL flagged `r sum(genus_mismatch$Situation=='Preferred', na.rm = T)` records where the author follows an alternative taxonomy, and flagged `r sum(genus_mismatch$Situation=='Internal_Error', na.rm = T)` record in error.

Excluding the previous records at the level of genus, BL flagged 75 binomials. Not all genera which where flagged in the previous step were identified in the last check, as BL may search for an epithet with a genus which was more similar to the non-target genus, and for which a binomial does not exist.

@@

```{r}
rm(genus_mismatch, genera_mispelled, family_incongruence)
```
